Programmer friendly communication framework

### 2024-03-09 2024_paper/paper/msglink_framework.tex
Addes citations

Like with HTTP, many languages provide simple APIs to create and use WebSocket connections.

@@

Socket.IO also further implements the abstractions outlined by goal 1) of a communication framework, by implementing automatic connection state management and reconnects. Where with WebSockets, the programmer explicitly needs to write code to \textbf{connect to a server},  \textbf{detect disconnects}, and repeat the procedure, with Socket.IO, the programmer is merely required to tell the computer to \textbf{"be connected to a specified server"}. The library will then connect, detect failures and reconnect automatically to satisfy this request.

@@

    \bibitem{b1} Proof for NordPass study, URL:https://tech.co/password-managers/how-many-passwords-average-person

>>>>

Like with HTTP, many languages provide simple APIs to create and use WebSocket connections. \cite{b3}

@@

Socket.IO also further implements the abstractions outlined by goal 1) of a communication framework, by implementing automatic connection state management and reconnects. Where with WebSockets, the programmer explicitly needs to write code to \textbf{connect to a server},  \textbf{detect disconnects}, and repeat the procedure, with Socket.IO, the programmer is merely required to tell the computer to \textbf{"be connected to a specified server"}. The library will then connect, detect failures and reconnect automatically to satisfy this request. \cite{b1}

@@

    \bibitem{b1} Information for Socket.io, URL:https://socket.io/
    \bibitem{b2} Information for Zod, URL:https://zod.dev/
    \bibitem{b3} Information for WebSocket++, URL: https://docs.websocketpp.org/ 
    https://github.com/zaphoyd/websocketpp/
